Reproducible Builds for\\ Computational Research Papers

### 2020-09-19 ms.tex
{make test}
{make test ARGS=--full}

\begin{table}[]
	\centering
	\caption{Makefile usage table.}
	\label{table:usagetable}
	\begin{tabular}{l|ll}
		\toprule
		\diagbox{\textbf{OPTION}}{\textbf{ARGS}} & \textbf{(empty)}              & \textbf{-{}-full}                    \\
		\midrule
		\textbf{(ms.pdf or empty)}          & debug/development    & release paper             \\
		\textbf{test}                       & test reproducibility & test reproducibility full \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\section{Example Use Case of RBs}
This sections provides a use case of RBs and also serves as a manual for creating reproducible \textit{papers} written in \LaTeX\ with Python as the \textit{results code} programming language.
For demonstration purposes we train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on MNIST~\cite{lecun2010mnist}, FashionMNIST~\cite{xiao2017fashion}, KMNIST~\cite{clanuwat2018deep} and QMNIST~\cite{yadav2019cold}.

@@

Regarding the \textit{results code} for Python, random seeds need to be set to a specific value such as:
\begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for some popular libraries.}, captionpos=b]
random.seed(0) # for build-in random module
np.random.seed(0) # for numpy
tf.random.set_seed(0) # for Tensorflow
# for pytorch
torch.backends.cudnn.benchmark = False
torch.backends.cudnn.deterministic = True
torch.cuda.manual_seed_all(0)
torch.manual_seed(0)
\end{lstlisting}

Using the random seeds and \textit{datatool} we could have deterministic stochasticity that reproduces figures, tables and variables.
For example Fig.~\ref{fig:image} depicts the train and validation loss for all datasets.
\begin{figure}[!t]
	\subfloat{\includegraphics[width=0.5\textwidth]{results/validation-loss}}
	\caption{Validation losses.
	Image example created from \textit{results code}.}
	\label{fig:image}
\end{figure}

@@

\begin{table}[h]
	\centering
	\caption{Table example created from results code.}
	\label{table:table}
	\setlength\tabcolsep{4.2pt}
	\input{results/metrics.tex}
\end{table}

>>>>

\begin{table}[]
	\centering
	\caption{Makefile usage table.}
	\label{table:usagetable}
	\begin{tabular}{l|l|l}
		\toprule
		\diagbox{\textbf{OPTION}}{\textbf{ARGS}} & \textbf{(empty)}              & \textbf{-{}-full}                    \\
		\midrule
		\textbf{(ms.pdf or empty)}          & debug/development    & release paper             \\
		\midrule
		\textbf{test}                       & test reproducibility & test reproducibility full \\
		\bottomrule
	\end{tabular}
\end{table}

@@

\section{Example Use Case of RBs}
This sections provides a use case of RBs and also serves as a manual for creating reproducible \textit{papers} written in \LaTeX\ with Python as the \textit{results code} programming language.
For demonstration purposes we train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on the following datasets:
\begin{itemize}
	\item MNIST~\cite{lecun2010mnist},
	\item FashionMNIST~\cite{xiao2017fashion},
	\item KMNIST~\cite{clanuwat2018deep},
	\item QMNIST~\cite{yadav2019cold},
	\item EMNIST~\cite{cohen2017emnist},
	\item CIFAR10~\cite{krizhevsky2009learning},
	\item CIFAR100~\cite{krizhevsky2009learning} and
	\item SVHN~\cite{netzer2011reading}.
\end{itemize}

@@

Regarding the \textit{results code} for Python, random seeds need to be set to a specific value such as:
\begin{lstlisting}[language=python, style=lststyle, caption={Python reproducibility commands for some popular libraries.}, captionpos=b]
# for build-in random module
random.seed(0)
# for numpy
np.random.seed(0)
# for tensorflow
tf.random.set_seed(0)
# for pytorch
torch.backends.cudnn.benchmark = False
torch.backends.cudnn.deterministic = True
torch.cuda.manual_seed_all(0)
torch.manual_seed(0)
\end{lstlisting}

Using the random seeds and \textit{datatool} we could have deterministic stochasticity that reproduces figures, tables and variables.
For example Fig.~\ref{fig:image} depicts the train and validation loss for all datasets.
\begin{figure}[!t]
	\subfloat{\includegraphics[width=0.25\textwidth]{results/MNIST-loss}}
	\subfloat{\includegraphics[width=0.25\textwidth]{results/FashionMNIST-loss}}
	\caption{Train and validation losses for MNIST and FashionMNIST.}
	\label{fig:image}
\end{figure}

@@

\begin{table}[h]
	\centering
	\caption{Table example created from results code.}
	\label{table:table}
	\setlength\tabcolsep{4.2pt}
	\scalebox{0.72}{\input{results/metrics.tex}}
\end{table}
